---
title: "Module 1, Part 1: Risk and Uncertainty"
linktitle: "M1.1: Uncertainty"
menu:
  content:
    parent: Module 1
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

Part 1 of Module 1 is all about risk and uncertainty. We will eventually use these concepts to study insurance markets and premiums.

## Objectives
- Calculate expected values and expected utility
- Define a risk pool
- Define risk aversion and diminishing marginal utility
 
## Activities
- Supplemental questions about insurance in the U.S., available [here](https://imccart.github.io/econ372-content/01-Insurance/preclass-01.html)
- Discussion of Humana and importance of risk pools on the [Module 1: Overview](/content/00-content.html) page
- In-class example on expected values
- In-class problem on expected costs, expected utilities, and risk aversion. The worksheet is [here](/resource/wksheet1.html).

## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ372-content/01-Insurance/01-insurance1.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/01-Insurance/01-insurance1.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/01-Insurance/01-insurance1.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
    

    