---
title: "Module 2: Physician Agency and Treatment Decisions"
linktitle: "M2: Overview"
menu:
  content:
    parent: Module 2
    weight: 1
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

The narrow goal of this module is to understand the role of physicians in making treatment decisions, and how the consequences of this may differ depending on the type of payment model employed. We'll finish the module with a discussion of current policy issues related to healthcare payments in the U.S.

The big picture economics concept of this module, or the "airport" idea that I hope you can remember several years later when we run into each other at the airport, is "behaviors can reflect both altruism and self interest." What does that mean? In the context of physician treatment decisions, it means that physicians and hospitals can pursue treatments that offer a benefit to patients but that also offer a financial benefit to them. These aren't mutually exclusive goals.


## Readings and other links

- <i class="fas fa-book"></i> Readings for this module:
    - Section 17.4 of [@pindyck2018]
    - Sections 5.3 and 17.2 of [@sloan2012]
    - [@mcguire2000]. Link to Chapter [here](https://www.sciencedirect.com/science/article/abs/pii/S1574006400801687)
    - [@gruber1996]. Link to paper [here](https://www.jstor.org/stable/2555794).
    - [@clemens2014]. **We'll discuss this paper at the end of the module.** Link to paper [here](https://www.aeaweb.org/articles?id=10.1257/aer.104.4.1320).
- <i class="fas fa-external-link-square-alt"></i> Supplemental information we'll use throughout this module.
    - [The Dartmouth Atlas](https://www.dartmouthatlas.org/interactive-apps/)
    - The Atlantic, December 2013, ["You're Getting Too Much Healthcare](https://www.theatlantic.com/health/archive/2013/12/youre-getting-too-much-healthcare/281896/)
    - MIT News Office, June 2018, ["The value of late-in-life health care spending"](http://news.mit.edu/2018/value-late-life-health-care-spending-medicare-0628)
    - [All About Medicare, Podcast](https://open.spotify.com/episode/11QshS7vlTptfBVkV8WkTG?si=sCnpjaDNT5mF3lDC6obB4g)
    - [All Aboud Medicaid, Podcast](https://open.spotify.com/episode/5wV95SFHGv9trpZrXACELP?si=DFnzeWj7R1eIv9w2Xr3PtQ)
    - [Healthcare Triage, Pay for Performance](https://www.youtube.com/watch?v=SFNuztrgQY0)
    - [NEJM Report, What is Pay for Performance](https://catalyst.nejm.org/doi/full/10.1056/CAT.18.0245)


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ372-content/02-Agency/02-agency0.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/02-Agency/02-agency0.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/02-Agency/02-agency0.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
    

    
