---
title: "Module 3: Hospital Pricing and Competition"
linktitle: "M3: Overview"
menu:
  content:
    parent: Module 3
    weight: 1
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

The narrow goal of this module is to understand hospital pricing, how we measure competition (in general, but also some specific aspects of health care markets), and how competition affects hospital/insurer negotiations.

The big picture economics concept of this module, or the "airport" idea that I hope you can remember several years later when we run into each other at the airport, is "profit matters, even for non-profits." What does that mean? In the context of hospitals (the majority of which are designated as not-for-profit entities), it means that hospitals still have to make some money. As one CEO put it regularly in my past life, "there's no mission without margin."

## Readings

- <i class="fas fa-book"></i> Readings for this module:
    - Section 5.4 of [@sloan2012]
    - [@reinhardt2006]
    - [@gaynor2015jel]
    - [@gaynor2017brookings]
    - [@cooper2019]. **We'll discuss this paper at the end of the module.**
- <i class="fas fa-external-link-square-alt"></i> Supplemental information we'll use throughout this module.
    - ["History of Cost Shifting"](https://theincidentaleconomist.com/wordpress/hospital-cost-shifting-brief-history-and-possible-future/)
    - Reinhardt, Uwe. 2006. ["The Pricing of US Hospital Services: Chaos Behind a Veil of Secrecy."](https://www.healthaffairs.org/doi/full/10.1377/hlthaff.25.1.57) *Health Affairs*, 25(1):57-69.
    - ["Value of tax breaks for non-profit hospitals doubled in a decade,"](https://www.washingtonpost.com/national/health-science/value-of-tax-breaks-for-nonprofit-hospitals-doubled-in-a-decade/2015/06/17/4162c640-1450-11e5-9ddc-e3353542100c_story.html) *Washington Post*, 2015
    - ["Nonprofit hospitals' community benefit requirements,"](https://www.washingtonpost.com/national/health-science/value-of-tax-breaks-for-nonprofit-hospitals-doubled-in-a-decade/2015/06/17/4162c640-1450-11e5-9ddc-e3353542100c_story.html) *Health Affairs* policy brief, 2016
    - [Health Care Pricing Project](https://healthcarepricingproject.org/)
    - [Health Care Cost Institute, Healthy Marketplace Index](https://healthcostinstitute.org/research/hmi-interactive)
    - ["Making healthcare markets work: Competition policy for health care"](https://www.brookings.edu/research/making-health-care-markets-work-competition-policy-for-health-care/)
    - [Hearing on health care consolidation and anticompetitive conduct](https://www.youtube.com/watch?v=c2rLy4FWn_g). Please focus just on the testimony of Martin Gaynor, as this is most relevant for our class. But if you're interested in pharmaceuticals, there is some great content in this video from other members of the panel as well.
    - [Hospital Billing](https://truecostofhealthcare.org/hospitalization/). This is a 6 minute video explaining some of the confusing aspects of hospital billing, which plays into what it really means to be a not-for-profit versus for-profit hospital.
    


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ372-content/03-Pricing/03-pricing0.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/03-Pricing/03-pricing0.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/03-Pricing/03-pricing0.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
