---
title: Syllabus
slug: syllabus
citeproc: true
bibliography: ../../static/bib/BibTeX_Library.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    toc: true
    fig_caption: false
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(googledrive)
library(dplyr)
library(tibble)
library(pander)
drive_download("bibliography/BibTeX_Library.bib", overwrite=TRUE, path='../../static/bib/BibTeX_Library.bib')
```

`r blogdown::shortcode("courseinfo")`

<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ372-content/syllabus-spring2023/syllabus.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of Syllabus</a></p>

## Course description

This course examines the industrial organization of health care markets in the U.S., including underlying theory, empirical findings, and related health care policy. We will focus specifically on insurance markets, informational asymmetries between physicians and patients, and hospital pricing.

**Prerequisites:** Economics 101 (Principles of Microeconomics). Some basic knowledge of calculus and derivatives is also required, but not necessarily the official Math 111 (Calculus I) course at Emory. 


## Learning outcomes

The broad goal of the class is to understand the structure of health care markets in the U.S. The course is designed around three areas, reflecting the different interactions an individual would have when navigating the health care system --- first choosing an insurance plan, then visiting a physician, and ultimately receiving hospital care. Our discussion of hospital care is further divided into issues of hospital objective functions, measuring hospital quality, and hospital competition and pricing. For each segment, we will examine underlying theoretical model(s), consider empirical evidence in the area, and discuss relevant health care policy. My specific goals are that, by the end of this course, you will be able to:

1. Explain the structure of the U.S. health care system, its main components, and its history

2. Model adverse selection in health insurance, examine its effects on health insurance markets, and support your arguments with existing data

3. Explain the physician agency problem, use a model of physician agency to examine financial incentives in health care, and summarize empirical evidence on the presence of physician agency

4. Describe hospital pricing, negotiation with insurers, and explain (qualitatively and quantitatively) the differences between charges and prices

5. Analyze hospital data in a real-life setting and predict effects of real-life policies

There are more specific learning outcomes for each module described on the relevant module's section of the [content page](/content/).

## Course materials

### Where to go
If you're here, then you know where to find our class website. Well done! Hopefully it's clear by the existence of the site that this is where I plan to host most of our information such as course materials, notes/slides, assignments. I'll also use Canvas to distribute any papers or specific readings that aren't available publicly, as well as post information that I don't want public like virtual meeting passwords (if needed) and grades. 


### Readings
There are two recommended textbooks for this class. One is an intermediate microeconomics textbook that will cover much of the basic economic theory, and another is a health economics textbook. We will supplement these textbooks with other readings listed below in the detailed schedule, as well as online presentations, policy papers, and videos.

  - @pindyck2018
  - @sloan2012
  
### Statistics software
Each assignment will generally include both a theoretical and empirical section. Most of the empirical work involves basic summary statistics. This can be done in just about any spreadsheet or statistics package. I'll use `R` for my work, but you are free to use whatever software you're most comfortable with. I encourage you to use `R` or `Python` simply because these are the most common programs used in applied data analysis right now, but you can certainly use Excel or Google Sheets if you'd prefer. This is **not** a statistics or econometrics class, so I do not expect you to have any statistics programming knowledge.

### Accessing data
For all assignments and in-class activities, I will house all of the links to the data on our class website, and I'll place the relevant datasets on Canvas. For transparency, I will also point you to other GitHub repositories where available. If you're new to Git or GitHub and want to understand some of that better, take a look at [Grant McDermott's](https://grantmcdermott.com/) notes on [Data Science for Economists](https://github.com/uo-ec607/lectures) as well as [Jenny Bryan's](https://jennybryan.org/) online reference book, [Happy Git and GitHub with R](https://happygitwithr.com/). But again, knowledge of Git or GitHub is not expected or required for this class.


### Turning things in
All assignments should be submitted as PDF files on Canvas. Since we'll be using some math in all of our answers, I suggest that assignments be completed through [Overleaf](https://www.overleaf.com/). As an Emory student, everyone has access to an institutional Overleaf account, which provides you with all the nice features of the product. You can use this to easily write PDF documents in a language known as "LaTeX". For a brief introductory video and links to more info, please see the video [here](https://www.overleaf.com/learn/latex/Questions/Getting_started_with_LaTeX_and_Overleaf_(formerly_writeLaTeX)). Overleaf is not a requirement, but I think it will save some you time in the long run. You are also welcome to use Word, Google Docs, LibreOffice, etc., and convert to PDF for your final submission.

The only **requirements** are that your submission is a PDF and that your answers are legible and organized. Please **DO NOT** write tiny answers in margins of papers, scan as PDF, and submit. I will deduct some points for these types of submissions.


## Course policies

**Be nice. Be honest. Don't cheat.**

Various policies for this course are described below. Basically, let's all work to be good citizens and take seriously our various roles as a student, teacher, friend, colleague, human, etc.

### Class meetings

All regular class meetings will take place in **White Hall, Room 103** on Mondays and Wednesdays from 11:30am to 12:45pm. 


### Office hours

My designated office hours will be on Monday and Wednesday from 1:30 to 2:30pm in R. Rollins, R432. I'm also available outside of these times. I just ask that you schedule an appointment in advance. [Make an appointment with me here.](https://mccarthy-meetings.youcanbook.me/) While we call these "office hours" they really should be "student hours". These are set times dedicated to all of you. This means that I will be in my office waiting for you to come by with whatever questions you have. Take a look at this video for a more interesting presentation of what office hours really are and why you should come!

<iframe src="https://player.vimeo.com/video/270014784" width="640" height="360" frameborder="0" allow="autoplay; fullscreen" allowfullscreen style="display: block; margin: 0 auto 1rem;"></iframe>

For any questions that you don't think need a meeting, you can always reach out to me through email. I do my best to respond within 24 hours to all emails.

### Academic integrity

The Emory University Honor Code is taken seriously and governs all work in this course. Details about the Honor Code are available at [Emory Honor Code](http://catalog.college.emory.edu/academic/policies-regulations/honor-code.html). By taking this course, you affirm that it is a violation of the code to cheat on exams, to plagiarize, to deviate from the instructions about collaboration on work that is submitted for grades, to give false information to a faculty member, and to undertake any other form of academic misconduct. You agree that the teacher is entitled to move you to another seat during examinations, without explanation. You also affirm that if you witness others violating the code you have a duty to report them to the honor council.

### Accessibility services

If you anticipate issues related to the format or requirements of this course, please meet with me. I would like us to discuss ways to ensure your full participation in the course. If you determine that accommodations are necessary, you may register with Accessibility Services at (404)727-9877 or via e-mail at accessibility@emory.edu. To register with OAS, students must self identify and initiate contact with the OAS office.

### Class-wide announcements

I will post regular announcements to the class on *Canvas*, so please set up your notifications on *Canvas* accordingly. I will also use *Canvas* to post all grades and any other information that needs to stay in the class. All other course materials will be available on our class website, [econ372s23.classes.ianmccarthyecon.com](https://econ372s23.classes.ianmccarthyecon.com).

### Lauren's Promise

**I will listen and believe you if someone is threatening you.**

Lauren McCluskey, a 21-year-old honors student athlete, [was murdered on October 22, 2018 by a man she briefly dated on the University of Utah campus](https://www.sltrib.com/opinion/commentary/2019/02/10/commentary-failing-lauren/). We must all take action to ensure that this never happens again.

If you are in immediate danger, call 911 or Emory police (404-727-6111).

Any form of sexual harassment or violence will not be excused or tolerated at Emory. If you are experiencing sexual assault, domestic violence, or stalking, please report it to me or directly to [Emory's Office of Respect](http://respect.emory.edu/index.html) (470-270-5360).


## Assignments and grades

Detailed descriptions of all assignments are on the [assignments page](/assignment/). Each assignment will contribute to your final grade as described below.

```{r assignments-grades, include=FALSE}
assignments <- tibble(
  Assignment = c("Weekly check-in", "Homework (60 x 3)", "Mid-term exam", "Final project"),  
  Points = c(20, 60*3, 60, 140)
)

assignments <- assignments %>%
  mutate(Percent = Points / sum(Points),
         Percent = scales::percent(Percent))

grading <- tibble(
  Grade = c("A","A-","B+","B","B-","C+"),
  Range = c("93-100%","90-92%","87-89%","83-86%","80-82%","77-79%"),
  Grade1=c("C","C-","D+","D","D-","F"),
  Range1=c("73-76%","70-72%","67-69%","63-66%","60-62%","< 60%")
)
```

<center>

```{r assignments-table, echo=FALSE, results="asis"}
pandoc.table(assignments, justify="lcc")
```

</center>

Your final percentage grade comes from your total points as a percent of all possible points available in the class (400). That percent then translates to a letter grade as follows:

<center>

```{r grades-table, echo=FALSE, results="asis"}
pandoc.table(grading, justify="lclc",
             col.names = c("Grade", "Range", "Grade", "Range"))
```

</center>